---
title: 'workingBrain: UK Biobank metadata.'
output:
  html_document:
    df_print: paged
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


## Setup and load data

```{r loadLibs, results="hide"}
library(readxl); library(tidyverse); library(dplyr); library(naniar); library(ggplot2); library(jsonlite);
library(data.tree); library(circlepackeR); library(igraph); library(ggraph);library(networkD3); library(htmlwidgets);
library(collapsibleTree); library(reticulate)
 
```


Load the data and have a look at the first few rows.
```{r loadData, echo=FALSE}
metaData_all <- read_excel("~/GoogleDrive/Git/raeBiobank/RR/workingBrain_dataFields.xlsx", 
    sheet = "allData_BB")

head(metaData_all)
```

This is all the datafields in the UK Biobank data set, so we need to filter for this specific study (i.e. based on the variable 'inBasket').
```{r filterData}
metaData<- filter(metaData_all, inBasket == T)
head(metaData)
```

## Explore
```{r checks1, echo=FALSE}
# Do we have the right number of rows? 
cat("How many rows does our dataframe have?\n")
nrow(metaData); 

cat("How many columns does our dataframe have?\n")
# Do we have the right number of columns?
ncol(metaData); 

# How many 'complete cases' (no rows/cols missing)?
cat("How many 'complete cases' (no rows/cols with NA)?\n")
sum(complete.cases(metaData))
```

**What's the structure of our data?**

This is currently held in the 'Path' variable. Will use this to create 'Medium' (Population vs Online vs Assessment Centre), 'MetaCat' and 'Category' variables (i.e. columns), making it more intuitive and removing some of the information that we're not really interested in (e.g. that that data was aquired through 'Touchscreen'). More details below.
```{r allPaths, echo=FALSE}
unique(metaData$Path)
```

**"Wrangling"**

The following are various steps to make the data more intuitive and easier to work with. The main aim is to divide the unhelpful (and in this state unusable) `Path` variable into columns that could actually help us make sense of the data. Details in the comments (probably lacking in some places, come back to this: `TODO`).

```{r splitPaths, results="hide"}

# Split "Path" column based on ">" separator
metaData_filtered <- metaData %>%
  rename(CategoryID = Category) %>% # Rename original "Category" column to what it actually is, i.e. "CategoryID"
  separate(Path, c("Medium", "CatVal1", "CatVal2","CatVal3", "CatVal4"), ">") # split "Path" column.
  

# Removing whitespace from vars.
metaData_filtered$Medium <- sub("^\\s+", "", metaData_filtered$Medium)
metaData_filtered$Medium <- sub("\\s+$", "", metaData_filtered$Medium)

metaData_filtered$CatVal1 <- sub("^\\s+", "", metaData_filtered$CatVal1)
metaData_filtered$CatVal1 <- sub("\\s+$", "", metaData_filtered$CatVal1)

metaData_filtered$CatVal2 <- sub("^\\s+", "", metaData_filtered$CatVal2)
metaData_filtered$CatVal2 <- sub("\\s+$", "", metaData_filtered$CatVal2)

metaData_filtered$CatVal3 <- sub("^\\s+", "", metaData_filtered$CatVal3)
metaData_filtered$CatVal3 <- sub("\\s+$", "", metaData_filtered$CatVal3)

metaData_filtered$CatVal4 <- sub("^\\s+", "", metaData_filtered$CatVal4)
metaData_filtered$CatVal4 <- sub("\\s+$", "", metaData_filtered$CatVal4)

# Change column values and structure in a way that makes sense.

metaData_filtered <- metaData_filtered %>%
  
  # Removing column values we won't need.
  replace_with_na_if(.predicate = is.character,condition = ~.x == "Touchscreen") %>% # remove "Touchscreen" column value from rows that contain them
  replace_with_na_if(.predicate = is.character,condition = ~.x == "Brain MRI") %>% # remove "Brain MRI" column value from rows that contain them
  replace_with_na_if(.predicate = is.character,condition = ~.x == "MET Scores") %>% # remove "Brain MRI" column value from rows that contain them
  replace_with_na_if(.predicate = is.character,condition = ~.x == "Reception") %>% # remove "Brain MRI" column value from rows that contain them
  
  mutate(CatVal1 = replace(CatVal1, CatVal1 == "Cognitive function online", "Cognitive function")) %>% # Replace 'Cognitive function online' with 'Cognitive function'
  mutate(CatVal1 = replace(CatVal1, CatVal1 == "Baseline characteristics" & is.na(CatVal2), "Sociodemographics_Baseline")) %>%
  mutate(CatVal1 = replace(CatVal1, CatVal1 == "Baseline characteristics" & CatVal2 == "Indices of Multiple Deprivation", "Sociodemographics")) %>%
  mutate(CatVal1 = replace(CatVal1, CatVal1 == "Ongoing characteristics", "Sociodemographics_Ongoing")) %>% # Replace 'Ongoing characteristics' with 'Sociodemographics'
  mutate(CatVal1 = replace(CatVal1, CatVal1 == "Baseline characteristics", "Sociodemographics")) %>% 
  # Replace 'Baseline characteristics' with 'Sociodemographics': Note that this is probably a bad way of doing this. It works for us out of luck (i.e. the spacing of 'Baseline characteristics' in the two separate cases) as we want to do two different things with them but if you want to do anywthing else with the data, this will likely lead to problems.
  mutate(CatVal1 = replace(CatVal1, is.na(CatVal1) & CatVal2 == "Psychosocial factors" & CatVal3 == "Mental health", "Mental health_Other")) %>%
  mutate(CatVal1 = replace(CatVal1, is.na(CatVal1) & CatVal2 == "Psychosocial factors" & CatVal3 == "Social support", "Mental health_Social support")) %>%
  replace_with_na_if(.predicate = is.character,condition = ~.x == "Psychosocial factors") %>%
  

  mutate(CatVal1 = replace(CatVal1,  CatVal1 == "Work environment" & CatVal2 == "Medical information", "Health and medical history")) %>%

  mutate(CatVal1 = replace(CatVal1, is.na(CatVal1) & CatVal2 == "Sociodemographics" & CatVal3 == "Employment", "Employment_Employment: Current")) %>%
  mutate(CatVal2 = replace(CatVal2, CatVal1 == "Employment_Current" & CatVal2 == "Sociodemographics" & CatVal3 == "Employment", "DELETEME")) %>%
  mutate(CatVal3 = replace(CatVal3, CatVal1 == "Employment_Current" & CatVal2 == "DELETEME" & CatVal3 == "Employment", "DELETEME")) %>%
  
  mutate(CatVal2 = replace(CatVal2, is.na(CatVal2) & CatVal1 == "Work environment", "Employment history")) %>% # Get rid of extra NAs that result from 'Work environment'
  mutate(CatVal1 = replace(CatVal1, CatVal1 == "Work environment" & CatVal2 == "Employment history", "Employment")) %>%
  
  mutate(CatVal2 = replace(CatVal2, CatVal1 == "Employment" & CatVal2 == "Employment history", "Employment: History")) %>%

  mutate(CatVal1 = replace(CatVal1, CatVal1 == "Verbal interview" & CatVal2 == "Medical conditions", "Health and medical history")) %>%
  mutate(CatVal1 = replace(CatVal1, CatVal1 == "Verbal interview" & CatVal2 == "Employment", "Employment")) %>%
  mutate(CatVal2 = replace(CatVal2, CatVal1 == "Employment" & CatVal2 == "Employment", "Other")) %>%
  
  mutate(CatVal1 = replace(CatVal1, CatVal1 == "Recruitment", "Sociodemographics_Baseline")) %>%

  unite("MetaCat", CatVal1:CatVal4) # put together all the columns previously split into "MetaCat" column.

# Remove all the "NA"s from the names.
metaData_filtered$MetaCat <- sub("NA_", "", metaData_filtered$MetaCat)
metaData_filtered$MetaCat <- sub("_NA", "", metaData_filtered$MetaCat)  


metaData_filtered <- metaData_filtered %>%
  separate(MetaCat, c("MetaCat", "Category"), "_") # split into "MetaCat" and "Category"

```

Following "wrangling", our data now has the following structure.
```{r}
head(metaData_filtered)
```

```{r splitPahts_show, echo=FALSE}
cat("Metacategories after transformation: \n")
unique(metaData_filtered$MetaCat)

cat("\nCategories after transformation: \n")
unique(metaData_filtered$Category)
```

```{r exportTransformedData}
# As .rda
# save(metaData_export, file = "metaData_export.rda")

#As csv
#write.csv(metaData_export,"/Users/munchausend/GoogleDrive/Git/raeBiobank/workingBrain_dataFields 210520.csv", row.names = TRUE)


```


## Visualize

### circlePacking
Circular packing or circular treemap allows to visualize a hierarchic organization. It is an equivalent of a treemap or a dendrogram, where each node of the tree is represented as a circle and its sub-nodes are represented as circles inside of it. \n\n

I thought this would be quite useful for visualising (and hopefully makign sense) of our 'metadata'. The size of the circles can be changed to be proportional to whatever value we choose, but for now I left it as constant as I couldn't really see any value that we could've made the size of the circles dependent on to help with insight.

**Visualising MetaCat/Cat relationship**

```{r circlePack_cats}
metaData_filtered$pathString <- file.path("world", metaData_filtered$MetaCat, metaData_filtered$Category)
metaData_filtered$value <- sample(seq(1:nrow(metaData_filtered)), 1)

cats_p <- circlepackeR(as.Node(metaData_filtered), size = "value", color_min = "rgb(250, 200, 150)", color_max = "rgb(120, 50, 0)")

cats_p

# save the widget
#saveWidget(cats_p, file=paste("circlePack_cats.html"))

```

**Visualising MetaCat/Cat/Fields relationship**

Note: had to use `FieldID` as opposed to `Field`(i.e. field name) to help with visualisation.
```{r circlePack_fields}
metaData_filtered$pathString <- file.path("world", metaData_filtered$MetaCat, metaData_filtered$Category, metaData_filtered$FieldID)
metaData_filtered$value <- sample(seq(1:nrow(metaData_filtered)), 1)

fields_p <- circlepackeR(as.Node(metaData_filtered), size = "value", color_min = "rgb(250, 200, 150)", color_max = "rgb(120, 50, 0)")

fields_p

# save the widget
# saveWidget(fields_p, file=paste("circlePack_fields.html"))
```

### Interactive Dendrogram

**There is some problem using two different types of html widgets in the same knit, so for now this will just live in the shiny app: https://munchausend.shinyapps.io/dataViz/**

```{r dendrogram_notZoomable}
# collapsibleTreeSummary(
#   metaData_filtered, c("MetaCat", "Category", "Field"),
#   root = 'UKBmetaData',
#   #width = 1200,
#   #height = 800,
#   zoomable = FALSE,
#   tooltip = TRUE,
#   )

```

### networkD3

```{r}
nodes <- read.csv("~/Downloads/sunbelt2019/Data files/Dataset1-Media-Example-NODES.csv")
links <- read.csv("~/Downloads/sunbelt2019/Data files/Dataset1-Media-Example-EDGES.csv")
```


```{r}
head(nodes)
head(links)
```


```{r}

links.d3 <- data.frame(from=as.numeric(factor(links$from))-1, 
                       to=as.numeric(factor(links$to))-1 )

nodes.d3 <- cbind(idn=factor(nodes$media, levels=nodes$media), nodes) 

```


```{r}
forceNetwork(Links = links.d3, Nodes = nodes.d3, Source="from", Target="to",
               NodeID = "name", Group = "type.label",linkWidth = 1,
               linkColour = "#afafaf", fontSize=12, zoom=F, legend=T,
               Nodesize=6, opacity = 0.8, charge=-300, 
               width = 600, height = 400, arrows = T)
```



```{r}
library('visNetwork') 
visNetwork(nodes, links, width="100%", height="400px")
```






